---
title: "Development Shiny Practical Work"
author: "Yolanda de la Hoz Simon"
date: "252015"
output: word_document
---

# Development of the shiny application

####Tasks:

0- Research of the available tools to develop the project (APARTE)

1- Data Preprocessing to get the data model

   1.1. Data collection
   1.2. Transform json and load the data in R
   1.3. Clean and filter the data

2- UI - View development 

   1.1. Composition and development of the different widgets in the ui.R file
   
3- UI - Controller development
    
   1.1. Development of the logic associated to each view
   1.2. Coordination of each view to create an integrate and reactive design

4- UI - General design testing      (APARTE)
    
   1.1. Visualization based tests
  ( of the general design, responsivness, response time)
  

### 1- Data Preprocessing to get the data model

####  1.1. Data collection

The train_data is in titanic.csv. The variable to predict is "Survived", it informs whether a passenger died in the accident or not. 

```{r}
```

####  1.2. Transform json and load the data in R

Remove unnecessary variables: literals, strings, ids, etc or variables with missing values.

```{r}
```

####  1.3. Clean and filter the data

```{r}
```


### 2- UI - View development 

####  1.1. Composition and development of the different widgets in the ui.R file

The train_data is in titanic.csv. The variable to predict is "Survived", it informs whether a passenger died in the accident or not. 

```{r}
```


### 3- UI - Controller development 

####  1.1. Development of the logic associated to each view

The train_data is in titanic.csv. The variable to predict is "Survived", it informs whether a passenger died in the accident or not. 

```{r}
```

####  1.2. Coordination of each view to create an integrate and reactive design

The train_data is in titanic.csv. The variable to predict is "Survived", it informs whether a passenger died in the accident or not. 

```{r}
```

